### 2018-04-28 paper/design.tex
yaaaay, outline figure

\subsection{Outline}

@@

\include*{building-blocks}
\include*{squad-overlay-design}
\include*{global-overlay-design}
\include*{message-passing}
\include*{file-exchange}

>>>>

This section presents the \name protocol in detail.
Our goal is to enable private and reliable file exchange between users participating in the system, by using their respective devices only.

The privacy objectives of our system require encryption primitives that we first detail in section~\ref{BuildingBlocks}.

The other constituents of \name are summarized in figure~\ref{fig:outline}.
On top, the devices of each user are circled in gray, and form a user's device squad. The squad online members communicate among themselves: they exchange files and messages information, and cooperate to predict the user's future behavior. This first protocol is called the \emph{squad overlay} and will be discussed in section~\ref{sec:squad_overlay}.
%On top we see that each user's devices (shown as clouds) communicate with one another through a dissemination protocol---coined the \emph{squad overlay}---that will be discussed in section~\ref{sec:squad_overlay}. 
Below, we see all devices connected in a random graph: each online device gives information about itself. This \emph{global overlay} will be covered in section~\ref{sec:global_overlay}.
The information brought by these overlays allows devices to securely and reliably exchange messages between users, as will be explained in section~\ref{sec:message_passing}.
Given this message passing protocol, users can privately exchange files. We will cover this ultimate goal in section~\ref{sec:file_exchange}.

\begin{figure}[t]
\centering
\def\svgwidth{\columnwidth}
%\input{outline.pdf_tex}
\import{figures/}{outline.pdf_tex}
%\includegraphics[width=0.9\columnwidth]{figures/outline.pdf}
\caption{\label{fig:outline}Outline of \name's components.}

\end{figure}

@@

\include*{building-blocks}
\include*{squad-overlay-design}
\include*{global-overlay-design}
\include*{message-passing-design}
\include*{file-exchange-design}
